Combinatorial interpretations of holonomic recurrences

### 2021-09-09 article/main.tex
Minor fix

Next, in Section~\ref{sec:known_results}, we present known results, i.e.~binary trees, unary-binary trees and Schröder trees. They demonstrate combinatorial interpretations that reflect different approaches.

>>>>

Next, in Section~\ref{sec:known_results}, we present known results, i.e.~interpretations for binary trees, unary-binary trees and Schröder trees. They demonstrate few different approaches to the problem.
